Generation of TypeScript Declaration Files from JavaScript Code

### 2019-12-30 ecoop-2020/main.tex
cleanup
abstract

\documentclass[a4paper,english,cleveref, autoref]{lipics-v2019}
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"

@@

%TODO mandatory: add short abstract of the document
\begin{abstract}
Developers are starting to write complex and large JavaScript applications in TypeScript, a typed superset of JavaScript. TypeScript applications integrate JavaScript libraries by including typed descriptions of their APIs called declaration files. These files are maintained manually, which is error prone and highly time consuming. Discrepancies between a declaration file and the JavaScript implementation will prevent developers from using them.

This work presents \lstinline{dts-generate}, a tool that generates a declaration file for JavaScript libraries uploaded to the NPM registry. It executes the library, gathers run-time information from the code examples written by the developers and generates the declaration file based on it. 244 declaration files were generated and compared against DefinitelyTyped, the standard public repository for declaration files. 33 files out of 244 had no differences.
\end{abstract}

@@

\bibliography{lipics-v2019-sample-article}

>>>>

\documentclass[a4paper,english,cleveref, autoref]{lipics-v2019}
% ECOOP 2020: 25 pages excluding references
%This is a template for producing LIPIcs articles. 
%See lipics-manual.pdf for further information.
%for A4 paper format use option "a4paper", for US-letter use option "letterpaper"
%for british hyphenation rules use option "UKenglish", for american hyphenation rules use option "USenglish"
%for section-numbered lemmas etc., use "numberwithinsect"
%for enabling cleveref support, use "cleveref"
%for enabling cleveref support, use "autoref"

@@

%TODO mandatory: add short abstract of the document
\begin{abstract}
Developers are starting to write complex and large applications in
TypeScript, a typed dialect of JavaScript. TypeScript applications
integrate JavaScript libraries via typed descriptions of their APIs
called declaration files. These files are available in public
repository DefinitelyTyped.
This repository is maintained manually, which
is error prone and time consuming. Discrepancies between a
declaration file and the JavaScript implementation lead to
incorrect feedback from the TypeScript IDE and thus to incorrect uses
of the underlying JavaScript library.

This work presents \lstinline{dts-generate}, a tool that generates
TypeScript declaration files for JavaScript libraries uploaded to the NPM
registry. It extracts code examples from the documentation written by
the developer, executes the library driven by the examples, gathers
run-time information, and generates a declaration file based on this
information. To evaluate the tool, 244 declaration files were generated and 
compared against the declaration file provided on DefinitelyTyped, the
standard public repository for declaration files. 33 files out of 244 had no differences. 
\end{abstract}

@@

\bibliography{main}
